---
title: "Code for figures and models"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(readxl)
library(ggplot2)
library(stargazer)
library(knitr)
library(dplyr)

windowsFonts(A = windowsFont("Garamond"))
theme_set(theme_classic(base_size = 12,  base_family="A"))
```

## Reading the data

The code chunk below pulls in the numbers from the EXCEL file. The variable names are the long form of the questions - so, below, I created a couple of shorter variable names to work with in document.

```{r data}
data<- read_excel("C:\\Users\\Nana Ama\\Desktop\\Trials\\Rstudio\\kwa.xlsx")

```

### Measuring Housing service satisfaction

The survey data from 2020 includes nineteen questions related to housing:

Two questions were recoded below so that the highest number is satisfied or strongly agree:

Is provincial delivery equitable across municipalities? (original coding: 1 strongly agree, 4 strongly disagree, 5 is Don't Know (124)) Is building houses the responsibility of the government to its citizens. (original coding: 1 strongly agree, 4 strongly disagree, 5 is Don't Know (47))

New variables: Housing equity 1=unsatisfied...4=satisfied Housing government: 1=unsatisfied...4=satisfied

Recoded to dummy variable: - Is housing one of "the most important problems that this country faces that the government should resolve?" (78/531 mention) (recoded to dummy 0=no 1=mentioned)

Not used: 16 out of the nineteen questions related to housing were not used.

```{r recode_housing}
# nineteen questions related to housing:Three of them used are below

#Is building houses the responsibility of the government to its citizens. (original coding: 1 strongly agree, 4 strongly disagree, 5 is Don't Know (47))
#Is provincial delivery equitable across municipalities? (original coding: 1 strongly agree, 4 strongly disagree, 5 is Don't Know (124))
# Is housing a most important problem?  (78/531 mention) (recoded to dummy)


# Recodes 5-response so 4 becomes 1 and 1 becomes 4...
data <-data %>%
 mutate(housing_equity=5-data$`78) Do you agree or disagree with the statement: The post-civil war public housing delivery was a transparent process; every citizen had a chance to acquire a house regardless of political affiliation. (Read out options)`, 
        housing_government=5-data$`81) Do you agree or disagree with the statement: It is the responsibility of the government to build houses for the citizens. (Read out options)`,
         housing_problem=data$`87) Housing ( In your opinion, what are the most important problems that this country faces that the government should resolve? (Write up to 3 problems))`
        ) 
data <- data %>%
  mutate(problem.dummy = if_else(data$housing_problem==6, 1, 0, 0))
```

The code chunk below recodes or identifies the variables:

-   ethnicity
-   province
-   party
-   neighborhood is central city or slum

```{r recode_invididual, echo=TRUE}
# Ethnicity
# Province
# Party
# Neighborhood - to construct urban vs. other
data$ethnicity<-data$`88) What is your ethnic group?`

data$party<-data$`90) If “YES”, which party is that?`
# Note that most of these are missing - respondent doesn't feel close to a party.

# I make the party a factor - meaning labels rather than numbers - are the labels attached to the correct numbers? 1=MPLA 2=UNITA, 7=some other party names...the number in parentheses is the number of people picking that party.
data$party<- factor(data$party,
levels = c(1,2,3,4,5,7), ordered=FALSE,
labels = c("MPLA (136)", "UNITA (46)", "CASE-CE (14)", "PRS (6)", "FNLA (4)", "Other (32)"))

# Province is available (5 provinces, already factor)
data$Province<-factor(data$Province, levels = c("Luanda", "Bengo", "Benguela", "Lunda Norte", "Malanje"))

# Central city vs slum
data<- data %>% mutate(slum=recode(Neigborhood, 
                                   "Centralidade do 44"=0,
                                   "Sanzala Grande" = 1,
                                   "Desvio" = 1,
                                   "Estação 44"=1,
                                   "Centralidade de Capari" =0,
                                   "Musseque Capari" = 1,
                                   "Musseque kikoca" =1,
                                   "Centralidade do Lobito" =0,
                                   "Lixeira"=1,
                                   "4 de Fevereiro"=1,
                                   "Downtown"= 0,
                                   "Centro da cidade"=0 ,
                                   "Cangambo ocidental"=0,
                                   "Bela fama"=1,
                                   "Camoma"=1,
                                   "Cafuco-fuco"=1,
                                   "Carreira de tiro"=1,
                                   "Centralidade do Mussungue"=0,
                                   "Samacaca"=0,
                                   "Estufa"=1,
                                   "Camaquenzo 2"=1,
                                   "Caita"=1))

```

### Service delivery: core compared to slums

The figures below measure satisfaction with housing services, comparing residents of slums to other urban residents - based on how satisfied people are with housing service received .(Higher scores indicate more satisfied)

All of the figures and models below use the "housing equity" variable created from question 78. You can create other water, electricity or other measures using the same approach and update the figures with those measures

```{r figure1, warning=FALSE, echo=TRUE, message=FALSE}
# Facet labels
place_names <- as_labeller(     c(`0` = "Urban center", `1` = "Slum"))
# The names above are used in the "facet_wrap" below
# if you delete the facet_wrap line you just get one plot by province

# This is the command to make the plot
ggplot (data, aes(x=Province, y=housing_equity))+
  geom_bar(stat = "summary", fun = "mean", fill="lightblue", color="red") +
  ylab("Service , Housing")+
  xlab("Province")+ 
  facet_wrap(data$slum, labeller=place_names) +
  ggtitle("Housing Equity, by province and place") 

ggplot (data, aes(x=Province, y=housing_government))+
  geom_bar(stat = "summary", fun = "mean", fill="lightblue", color="red") +
  ylab("Government responsibility , Housing")+
  xlab("Province")+ 
  facet_wrap(data$slum, labeller=place_names) +
  ggtitle("Housing as government responsibility, by province and place")


```

### Service delivery and province

```{r figure2, warning=FALSE, echo=TRUE, message=FALSE}
ggplot (data, aes(x=Province, y=housing_equity))+
  geom_bar(stat = "summary", fun = "mean", fill="lightblue", color="red") +
  ylab("Service , housing")+
  xlab("Province")+
  ggtitle("Housing equity, by province") 
```

## Service delivery and political affiliation

The factor labels show the party name and number of people who are in that party in the sample. NA means no party preference given.

There doesn't seem to be any meaningful variation.

```{r figure3, warning=FALSE, echo=TRUE, message=FALSE}
ggplot (data, aes(x=party, y=housing_equity))+
  geom_bar(stat = "summary", fun = "mean", fill="lightblue", color="red") +
  ylab("Service , Housing")+
  xlab("party")+
  ggtitle("Housing equity, by party") 
```

## Models to confirm

The model just uses the political party, slum vs central, and province, jointly, to estimate impacts on equity

Positive coefficients in the first table indicate higher levels of equity

Party and province don't matter for housing equity, only slum vs. central city.

The baseline categories for party is the MPLA and the baseline category for province is Luanda

```{r model1, warning=FALSE, comment=""}
model1<-lm(housing_equity~party+Province+slum, data=data)
model2<-lm(housing_government~party+Province+slum, data=data)
stargazer(model1,model2, type="text", style="apsr")
```
